\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Article Title}

### 2013-12-13 paper/paper.Rnw
changed to utf8 + small edits

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

@@

@@

\author{
\large
\textsc{John Smith}\thanks{A thank you or further information}\\[2mm] % Your name
\normalsize University of California \\ % Your institution
\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
\vspace{-5mm}
}
\date{}

@@

>>>>

\usepackage[sc]{mathpazo} % Use the Palatino font
%\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage[utf8]{inputenc}
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

@@

\usepackage{color} % used to mark parts that need to be edited

@@

\author{
\large
\textsc{Oliver Hümbelin}\\[2mm] % Your name
\normalsize Bern University of Applied Sciences \\ % Your institution
\normalsize \href{mailto:oliver.huembelin@bfh.ch}{oliver.huembelin@bfh.ch} % Your email address
\vspace{5mm}\\
\large
\textsc{Rudolf Farys}\\[2mm] % Your name
\normalsize University of Bern \\ % Your institution
\normalsize \href{mailto:rudolf.farys@soz.unibe.ch}{rudolf.farys@soz.unibe.ch} % Your email address
\vspace{-5mm}
}
\date{}

@@

%%%-------------------------------------------------%%%
%%% How did inequality change over time %%%
%%%-------------------------------------------------%%%

<<subdoc_content_introduction, child='subdocuments/change.Rnw', eval=T>>=
@
